Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-29 paper/gd1.tex
redundant

We extract properties of the stream from the stream region defined above as a
function of $\phi_1$ by computing properties in overlapping windows:
we set the window size to $XX^\circ$ in $\phi_1$, and shift the window center by
$1^\circ$ along the stream region.
\figurename~\ref{fig:track-and-model} shows the median latitude, $\phi_2$,
stream surface density, $XX$, stream width, $XX$, and median proper motions,
$\mu_{\phi_1}$ and $\mu_{\phi_2}$, extracted in this way.
For the surface density, we subtract an estimate of the background surface
density by \todo{AB}.
To estimate the stream width, $w$, we compute the median absolute deviation,
$\textrm{MAD}$, and use this to estimate a robust standard deviation, $w = 1.5
\times \textrm{MAD}$.

>>>>

We extract properties of the stream from the region defined above as a function
of $\phi_1$ by computing properties in overlapping windows:
we set the window size to $XX^\circ$ in $\phi_1$, and shift the window center by
$1^\circ$ along the stream region.
\figurename~\ref{fig:track-and-model} shows the median latitude, $\phi_2$,
stream surface density, $XX$, stream width, $XX$, and median proper motions,
$\mu_{\phi_1}$ and $\mu_{\phi_2}$, extracted in this way.
For the surface density, we subtract an estimate of the background surface
density by \todo{AB}.
To estimate the stream width, $w$, we compute the median absolute deviation,
$\textrm{MAD}$, and use this to estimate a robust standard deviation, $w = 1.5
\times \textrm{MAD}$.
